Modern Byte Pair Tokenizers are Zipfian

### 2025-05-14 writeup/paper.tex
added belevich paper

Noticeable theoretical work has been done in service of explaining Zipf's law for language \cite{li1992}. Most significant was Belecitch's \textit{On the statistical laws of linguistic distributions}\cite{Belevitch1959}, in which the author shows the first order approximation of the rank ordering of many statistical distributions are all Zipfian. Can this approximation be shown to be invariant under the byte pair encoding transformation?

>>>>

Noticeable theoretical work has been done in service of explaining Zipf's law for language \cite{li1992}. Most significant was Belevitch's \textit{On the statistical laws of linguistic distributions}\cite{Belevitch1959}, in which the author shows the first order approximation of the rank ordering of many statistical distributions are all Zipfian. This indicates that Zipf's law may be due to the rank ordering of words more than the underlying formation of language, which is what Zipf was originally interested in. Can Belevitch's proof be shown to be invariant under the byte pair encoding transformation?
